Bip32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-05-06 paper.tex
exponents

The paper specifies $j \leq 2^{20}$, allowing for a maximum 1048576 levels of derivation, such that $a_{j} \leq 2^{254} + 2^{253} + 2^{247}$ - a form suitable for our purposes.

@@

It also becomes apparent that the recommended maximum level of depth in the BIP32-Ed25519 paper, $2^{20}$, is lower than the actual number of levels that can be performed without bit overflows, $2^{26}$. Indeed, $a_{j} \leq 2^{254} + 2^{253} + 2^{247} < 2^{254} + 2^{253} + 2^{252}$.
\section{Implementations}

>>>>

The paper specifies $j \leq 2^{20}$, allowing for a maximum 1048576 levels of derivation, such that $a_{j} \leq 2^{254} + 2^{253} + 2^{227 + 20 = 247}$ - a form suitable for our purposes.

@@

It also becomes apparent that the recommended maximum level of depth in the BIP32-Ed25519 paper, $2^{20}$, is lower than the actual number of levels that can be performed without bit overflows breaking the scalar's Ed25519-compatibility: $2^{26}$. Indeed, $a_{j} \leq 2^{254} + 2^{253} + 2^{247} < 2^{254} + 2^{253} + 2^{227+26=253}$.
\section{Implementations}
